On Supporting Molecular Visualization on Grid Resources using Visual Programming Environments

### 2008-04-24 opal/documents/grid2008/paper.tex
added a few more diagrams

\section{Intro on scientific workflows and grid computing}

@@

@@

@@

@@

% TODO: possibly expand every bullet
\begin{itemize}
\item{Focus on application-level services}
\item{Provide users access to virtualized resources}
\item{Provide multiple user interfaces to scientific users}
\item{Lower deployment costs}
\item{Follow the Web 2.0 paradigm by enabling user participation and contribution}
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{architecture}
\end{center}
\caption{Services Oriented Science Using the Opal Toolkit}
\label{fig:arch}
\end{figure}

@@

\begin{itemize}
\item{Scheduling and Cluster Management}
\item{Data management and Persistence}
\item{Security}
\item{Standardized WSDL API}
\item{Argument Description and Dynamic Interface Generation}
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{opal-gui}
\end{center}
\caption{Service Invocation via the Opal GUI}
\label{fig:opal-gui}
\end{figure}

@@

\section {Service based workflows}

@@

@@

\section {Discussion - Workflow modeling and execution}

@@

%% References
\bibliographystyle{plain}
\bibliography{paper}

>>>>

\section{Introduction}

@@

% TODO: Add more context

@@

% TODO: Add Grid stuff

@@

% TODO: Need a more useful screenshot
\begin{figure}
\begin{center}
\includegraphics[width=8cm]{vision-overview}
\end{center}
\caption{A typical scientific workflow composed using the Vision interface}
\label{fig:vision-overview}
\end{figure}

@@

% TODO: possibly expand every bullet (04/23)
\begin{enumerate}
\item{Focus on application-level services}
\item{Provide users access to virtualized resources}
\item{Provide multiple user interfaces to scientific users}
\item{Lower deployment costs}
\item{Follow the Web 2.0 paradigm by enabling user participation and contribution}
\end{enumerate}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8.5cm]{architecture}
\end{center}
\caption{Services Oriented Science using the Opal Toolkit}
\label{fig:arch}
\end{figure}

@@

% TODO: Expand (04/23)
\begin{enumerate}
\item{Scheduling and Cluster Management}
\item{Data management and Persistence}
\item{Security}
\item{Standardized WSDL API}
\item{Argument Description and Dynamic Interface Generation}
\end{enumerate}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8.5cm]{opal-gui}
\end{center}
\caption{Service Invocation via the Opal GUI}
\label{fig:opal-gui}
\end{figure}

@@

\section {Services-based Workflows in Vision}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{vision-gui}
\end{center}
\caption{Automatic interface generation for the PDB2PQR service in Vision}
\label{fig:vision-gui}
\end{figure}

@@

% TODO: Need a more accurate screenshot
\begin{figure}
\begin{center}
\includegraphics[width=8cm]{vision-workflow}
\end{center}
\caption{Vision worklow using local and remote services}
\label{fig:vision-workflow}
\end{figure}

\section {Discussion}

@@

%% References
% TODO (04/23)
\bibliographystyle{plain}
\bibliography{paper}
